Figures

### 2019-07-18 figures/07_model-selection.Rmd
show all horseshoe results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 5, eval = TRUE, warning = FALSE, message = FALSE)
# setwd("figures")
source("../scripts/99_utils.R")
```

@@

```{r tp_summary, fig.width=4, fig.height=4.25}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[1]] # 1 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

# plot tp model fixed effects summary
# summary(fit_tp)
gg_tp <- spread_draws(fit_tp, 
                     b_maxdepth, 
                     b_hu12vbaseflowvmean, 
                     b_phosphorusvfertilizervuse, 
                     b_buffervcultivatedvcrops) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  mutate(key = factor(pretty, levels = c("Max depth", 
                     "Baseflow", 
                     "Fertilizer P input", 
                     "Buffer Ag"))) %>%
  group_by(key) %>%
  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = key, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) +
  xlab("")

gg_tp_fe

@@

```{r tn_summary, fig.height=4, fig.width=4.25}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, 
                     b_maxdepth, 
                     b_soilvorgvcarbon, 
                     b_nitrogenvfertilizervuse, 
                     b_buffervcultivatedvcrops) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  mutate(key = factor(pretty, levels = c("Max depth", 
                     "Soil organic carbon", 
                     "Fertilizer N input", 
                     "Buffer Ag"))) %>%
  group_by(key) %>%
  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

gg_tn_fe <- ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = key, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) +
  xlab("")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", eval = TRUE, warning = FALSE, message = FALSE)
# setwd("figures")
source("../scripts/99_utils.R")
```

@@

```{r tp_summary, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[1]] # 1 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

# plot tp model fixed effects summary
# summary(fit_tp)

b_vars <- stringr::str_subset(
  tidybayes::get_variables(fit_tp), 
  c("^(b_)(?!.*Intercept).*$"))

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) +
  xlab("")

gg_tp_fe
```

@@

```{r tn_summary, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

gg_tn_fe <- ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) +
  xlab("")
